%-------------------------
% Resume in Latex
% Author : Amit Rakte
% Based off of: https://github.com/Ameet-Rakte/Resume_Latex_Based
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \textbf{\Huge \scshape Amit Rakte} \\ \vspace{1pt}
    \small +91 7770081004 $|$ \href{official.amitrakte@gmail.com}{{official.amitrakte@gmail.com}}    \\ 
    \small  \href{http://linkedin.com/in/amitrakte/}{\bf LinkedIn} $|$
    \href{http://github.com/Ameet-Rakte}{\bf GitHub} 
    
\end{center}
% \href{https://www.youtube.com/channel/UCacvJAgrPTjSEdnZObMzpqQ}{\bf YouTube}

%-----------PROFILE-----------
\section{Profile}
\begin{itemize}[leftmargin=0.15in, label={}]
\item 
Strong analytical background with hands-on experience in interpreting data, optimising processes, and ensuring data accuracy in analyst roles at \textbf{eClerx and Verificient Technologies}. Have gained good exposure to understanding various aspects of \textbf{Full Stack Java Development} through the master’s program. Looking to leverage Analytical and Software Development skills in a dynamic and challenging environment where I can share my skills and expand my capabilities further in the pursuit of progressive career advancement.
\end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{\hspace{0.2cm} : Java, HTML, CSS, JavaScript/TypeScript} \\
     \textbf{Frameworks}{\hspace{2.45cm} : Salesforce, Spring boot, CRM, Angular, Hibernate, Spring MVC, REST API’s } \\
     \textbf{Database}{\hspace{2.95cm} : Oracle, MySQL, Spring Data JPA, DDL, DML} \\
     \textbf{Software Tools}{\hspace{2cm} : Airtable, Eclipse IDE, VS Code, Spring tool Suite, GIT, Maven } \\
     \textbf{Familiar Subject}{\hspace{1.66cm} : Data Science, Data Structure and Algorithm, Operating System, DBMS}\\     
    }}
 \end{itemize}

% \section{Technical Skills}
% \begin{itemize}[left=0.15in, label={}]
%     \item \textbf{Programming Languages:} Python, SQL, Scala
%     \item \textbf{Big Data Technologies:} Spark, PySpark, Spark SQL, YARN, Kubernetes, Hadoop, Hive, Impala
%     \item \textbf{Data Engineering Tools:} Azure Devops, Data Modelling, ETL/ELT data Pipeline
%     \item \textbf{Orchestration:} Airflow, Kubernetes, CA Autosys
%     \item \textbf{Familiar:} FastAPI, Elasticsearch, ADF, ADLS, Azure Blob, Amazon S3, Databricks
%     \item \textbf{Developer Tools:} Git, VS Code, Visual Studio, PyCharm, IntelliJ
% \end{itemize}

%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
% -------------------------------------------

    \resumeSubheading
      {eClerx}{April 2025 - Present}
      {Analyst}{Pune, India}
      \resumeItemListStart
      \resumeItem{Handle day-to-day data operations with accuracy and attention to detail.}
      \resumeItem{Maintain documentation and knowledge bases to support internal training and process consistency.}
        % \item Developed an automated invoicing system, enabling dynamic pricing adjustments on cloud service provider invoices.
        \resumeItem {Collaborate with cross-functional teams including \textbf{data engineers, marketers, and business stakeholders.}}
        \resumeItem {Uphold confidentiality and compliance standards, especially in financial or client-sensitive data.}
    \resumeItemListEnd
    
     \resumeSubheading
      {Simplilearn}{September 2022 - March 2023}
      {Full Stack Java Developer}{Pune, India}
      \resumeItemListStart
        \resumeItem {Design \& Develop the Application using \textbf{Spring REST Framework}.}
       
        \resumeItem{Designed and implemented advanced development capabilities using \textbf{Angular, Custom tags, and CSS}}to develop the front-end UI pages.
         \resumeItem {Worked on Hibernate to interact with \textbf{MySQL database} tables by using \textbf{CRUD operations.}}
        \resumeItem{Involved in the Analysis, Design, and Development phases of \textbf{SDLC Life-cycle.}}
      \resumeItemListEnd

    \resumeSubheading
      {Verificient Technology Private Limited}{March  2022 - September 2022}
      {Data Analyst}{Pune, India}
      \resumeItemListStart
        \resumeItem {Analysed more than 30,000 customer sales data to find the bottlenecks in the business process.}
        \resumeItem {Worked as Salesforce Admin and got exposure to the sales cloud.}
        \resumeItem {Interpreting data, analyzing results using statistical techniques.}
        \resumeItem {Developing and implementing data analyses, data collection systems and other strategies that optimize statistical efficiency and quality.}

% Optimized overall process performance through \textbf{Spark performance tuning}, managing a vast dataset of \textbf{15Terabyte(TB)}.

      \resumeItemListEnd

      \resumeSubheading
      {CWS Technology}{November 2021 - February 2022}
      {Java Developer Intern}{Pune, India}
      \resumeItemListStart
        \resumeItem {Designing, maintaining and building the reusable, efficient and reliable Java code.}
        \resumeItem {Implementing the Design Patterns like \textbf{Spring MVC} to improve the performance. }
        \resumeItem {Assisting in maintaining and updating existing applications and modules. }
        \resumeItem {Implementing GIT for version control.}


        
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Padmabhushan Vasantdada Patil Institute of Technology, Pune}{Pune, Maharashtra}
      {Bachelors in Computer Science and Engineering}{July 2017 - June 2022}
      \resumeSubheading
      {Katruwar Kabra Mantri College, Manwath}{Manwath, Maharashtra}
      {Senior Secondary School}{April 2015 - Mar 2017}
    
  \resumeSubHeadingListEnd
%-------------------------------
%
\end{document}
